### 2015-06-01 doc/thesis/typedlua.tex
Minor improvements in the thesis text

Typed Lua allows the assignment \texttt{v = v or e} to change
the type of \texttt{v} from \texttt{t|nil} to \texttt{t}
if it matches the following rules: 
the type of \texttt{e} is a subtype of \texttt{t},
and the variable \texttt{v} is local to the current function
and it is not being assigned in another function.
The change only affects the type of \texttt{v} in the remainder
of the current scope.
Any assignment to \texttt{v} restores its type back to the
original type.
In the case of \texttt{greeting}, the assignment change its type
from \texttt{string|nil} to \texttt{string}.

@@

When Typed Lua finds the predicate $\texttt{v[e}_{\texttt{1}}\texttt{] == e}_{\texttt{2}}$,
it checks whether the type of the variable \texttt{v} is an union of table types,
whether the type of $\texttt{e}_{\texttt{1}}$ is a literal type $\texttt{l}_{\texttt{1}}$,
and whether the type of $\texttt{e}_{\texttt{2}}$ is a literal type $\texttt{l}_{\texttt{2}}$.
If that is the case, it constrains the type of \texttt{v} inside
the \texttt{if} to the table type that has a key of type
$\texttt{l}_{\texttt{1}}$ which maps to a value of type $\texttt{l}_{\texttt{2}}$.
In our example, the expression \texttt{e.tag == "Add"} makes Typed Lua
constrain the type of \texttt{e} to \texttt{\{"tag":"Add", 1:Exp, 2:Exp\}}.
If we did not add this special predicate, we would not be able to traverse an AST,
as any attempt to index an union raises a compile-time warning.

>>>>

Typed Lua allows the assignment \texttt{v = v or e} to change
the type of \texttt{v} from \texttt{t|nil} to \texttt{t}
if it matches the following rules: 
the type of \texttt{e} is a subtype of \texttt{t},
and the variable \texttt{v} is local to the current function
and it is not being assigned in another function.
The change only affects the type of \texttt{v} in the remainder
of the current scope.
Any assignment to \texttt{v} restores its type back to the
original type.
In the case of \texttt{greeting}, the assignment changes its type
from \texttt{string|nil} to \texttt{string}.

@@

When Typed Lua finds the predicate $\texttt{v[e}_{\texttt{1}}\texttt{] == e}_{\texttt{2}}$,
it checks whether the type of the variable \texttt{v} is an union of table types,
whether the type of $\texttt{e}_{\texttt{1}}$ is a literal type $\texttt{l}_{\texttt{1}}$,
and whether the type of $\texttt{e}_{\texttt{2}}$ is a literal type $\texttt{l}_{\texttt{2}}$.
If that is the case, it constrains the type of \texttt{v} inside
the \texttt{if} to the table type that has a key of type
$\texttt{l}_{\texttt{1}}$ which maps to a value of type $\texttt{l}_{\texttt{2}}$.
In our example, the expression \texttt{e.tag == "Add"} makes the Typed Lua
compiler constrain the type of \texttt{e} to \texttt{\{"tag":"Add", 1:Exp, 2:Exp\}}.
If we did not add this special predicate, we would not be able to traverse an AST,
as any attempt to index an union raises a compile-time warning.
